---
title: "Vector Operations in R"
author: "Dang Nghiem Vo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# `intersect()` Function

The `intersect()` function returns the common elements between two vectors. Here's an example:

```{r}
# Example: Finding common elements between two vectors
vec1 <- c(1, 2, 3, 4, 5)
vec2 <- c(3, 4, 5, 6, 7)
common_elements <- intersect(vec1, vec2)
common_elements
```

# `setdiff()` Function

The `setdiff()` function returns the elements in the first vector that are not present in the second vector. Here's an example:

```{r}
# Example: Finding elements unique to vec1
unique_to_vec1 <- setdiff(vec1, vec2)
unique_to_vec1
```

# `union()` Function

The `union()` function returns all unique elements from both vectors. Here's an example:

```{r}
# Example: Combining unique elements from vec1 and vec2
all_unique_elements <- union(vec1, vec2)
all_unique_elements
```

# `setequal()` Function

The `setequal()` function checks if two vectors have the same elements, regardless of their order. Here's an example:

```{r}
# Example: Checking if vec1 and vec2 have the same elements
are_equal <- setequal(vec1, vec2)
are_equal
```

# `unique()` Function

The `unique()` function returns the unique elements of a vector. Here's an example:

```{r}
# Example: Finding unique elements in a vector
vec_with_duplicates <- c(1, 2, 2, 3, 3, 3, 4, 4, 5)
unique_elements <- unique(vec_with_duplicates)
unique_elements
```